\documentclass[a4paper, 10pt]{article}

\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[sc]{mathpazo}

% Various spacing parameters
\usepackage{microtype}
\usepackage[margin=3.5cm]{geometry}
\linespread{1}
\parindent 0pt
\parskip 4pt

% Spacing inside description environment
\usepackage{enumitem}  
\setlist[description]{style=multiline,leftmargin=.8cm,parsep=4pt}

\title{Fluid Dynamics + Turbulence (fall 2017) \\ Homework Problems I}
\author{}
\date{}

%----------------------------------------------------------------------------------------

\begin{document}
\maketitle

\large{
\textbf{Posted:}
\today.

\bigskip
\textbf{Deadline for submission of homework problem:}

Tuesday September 11 at 08:30 am (on Blackboard).
}

\bigskip
%\tableofcontents



%\newpage

\section[Homework problem 1]{Homework problem 1.1: Modeling and optimisation of a one-dimensional wind farm}

Read the paper J.\ Herp et.al.: {\it Wind-farm power optimisation including flow variability}, Renewable Energy 81 (2015) 173-81, and learn about the Jensen wake model with the Katic wake superposition and the sequential optimisation.

\begin{description}
\item[(a)]
Implement the Jensen wake model with Katic superposition for a one-dimensional wind farm with $N$ turbines, equidistant turbine spacing $\Delta{x}$ and aligned wind direction.

\item[(b)]
Determine the turbine powers $P_i$ for the Betz induction factors $q_i=1/3$ ($1\leq i\leq N=10$). Use $u_0=10$m/sec, $\Delta{x}=12R$ and $k=0.04$. Produce a figure showing your results.

\item[(c)]
Implement the sequential optimisation, and determine the optimised induction factors $q_i^\mathrm{sopt}$ and turbine powers $P_i$ ($1\leq i\leq N=10$). Produce figures showing your results.

\item[(d)]
Apply a standard MATLAB optimisation routine, and determine the optimised induction factors $q_i^\mathrm{opt}$ and turbine powers $P_i$ ($1\leq i\leq N=10$). Produce figures showing your results.

\item[(e)]
Compare your results from (d) with those from (b) and (c).

\item[(f)]
Discuss the solutions $q_i$, $P_i$ as a function of $N=5$/10/20 and $k\Delta{x}/R$ with e.g.\ $k=0.02$/0.04/0.07 and/or $\Delta{x}/R=8$/12/16.
\end{description}

\end{document}